### 2015-02-02 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Updated Text

@@

SPRAY DENSITY MEASURES

@@

GAS LAYER COOLING

FIRE SUPPRESSION

@@

@@

>>>>

\section{Experiment Descriptions}
\label{sec:Experiment_Descriptions}

@@

\subsection{Spray Density Measures}
\label{sec:Spray_Density_Measures}

@@

\subsection{Gas Cooling}
\label{sec:Gas_Cooling}

\subsection{Fire Suppression}
\label{sec:Fire_Suppression}

@@

The series of tests described within this report were conducted at the Delaware County Emergency Services Training Center, located in Sharon Hill, PA. A burn building as well as two purpose built concrete structures are located on the grounds of the ESTC. The burn building was used for the gas cooling experiments and the purpose built concrete structures were used for the fire suppression experiments.

@@

The burn building is a purpose-built live fire training structure comprised of both a two story and three story section. The building is supported with reinforced concrete beams and columns.  The floors and ceilings are also concrete with the interior walls constructed of cement block. The walls and ceiling of the burn rooms within the structure are protected with a 25 mm thinck layer of calcium silicate insulation, which is covered by a 50 mm thick concrete tile. The floor of the burn rooms is protected with fire brick.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/burnbuilding}
	\caption{Delaware County, PA Burn Building}
	\label{fig:Delaware_County,_PA_Burn_Building}
\end{figure}

The two room configuration within the burn building had overall dimensions of 6.5 m (21.3 ft) by 9.2 m (30.2 ft). The burn room where the fuel load was located measured 3.8 m (12.5 ft) by 5.7 m (18.7 ft) with a ceiling height of 3.35 m (11.0 ft). The adjacent room where the water was applied for gas cooling measured 4.1 m (13.4 ft) by 5.7 m (18.7 ft), also with a ceiling height of 3.35 m (11.0 ft). The open door from the adjacent room to the exterior measured 2.0 m (6.5 ft) high and 0.9 m (2.9 ft) wide.
